Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)

### 2018-10-16 paper/paper.Rmd
started creating the Shiny app

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)

@@

# Clean the Hamby 224 set 11 data
hamby224_set11_cleaned <- hamby224_set11 %>%
  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
  rename(bullet1 = bulletA,
         bullet2 = bulletB, 
         land1 = landA,
         land2 = landB) %>%
  mutate(study = factor("Hamby_224"), 
         set = factor("2"),
         bullet1 = recode(factor(bullet1), 
                          "Bullet 1" = "1", 
                          "Bullet 2" = "2", 
                          "Bullet I" = "I"),
         bullet2 = recode(factor(bullet2), 
                          "Bullet 1" = "1", 
                          "Bullet 2" = "2", 
                          "Bullet I" = "I"),
         land1 = recode(factor(land1), 
                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
         land2 = recode(factor(land2), 
                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6")) %>%
  select(study, set, bullet1:land2, rf_features, rfscore, samesource)

>>>>

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, cache = TRUE)

@@

# Clean the Hamby 224 set 11 data
hamby224_set11_cleaned <- hamby224_set11 %>%
  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
  rename(bullet1 = bulletA,
         bullet2 = bulletB, 
         land1 = landA,
         land2 = landB) %>%
  mutate(study = factor("Hamby_224"), 
         set = factor("11"),
         bullet1 = recode(factor(bullet1), 
                          "Bullet 1" = "1", 
                          "Bullet 2" = "2", 
                          "Bullet I" = "I"),
         bullet2 = recode(factor(bullet2), 
                          "Bullet 1" = "1", 
                          "Bullet 2" = "2", 
                          "Bullet I" = "I"),
         land1 = recode(factor(land1), 
                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6"),
         land2 = recode(factor(land2), 
                        "Land 1" = "1", "Land 2" = "2", "Land 3" = "3", 
                        "Land 4" = "4", "Land 5" = "5", "Land 6" = "6")) %>%
  select(study, set, bullet1:land2, rf_features, rfscore, samesource)
